Supplementary material

### 2023-05-15 analyses/scripts/full_data_extraction_citation_table.Rmd
Finally, a working version of the supplementary tables

---
output: 
  pdf_document:
    df_print: kable
    latex_engine: xelatex
    keep_tex: true
---
```{r setup, include=FALSE}
# options(kableExtra.auto_format = FALSE,
#         knitr.table.format = "latex"
#         )

knitr::opts_chunk$set(echo = FALSE, 
                      include = FALSE,
                      # dev = 'jpeg', 
                      fig.width = 8, 
                      fig.height = 6, 
                      message = FALSE,
                      warning = FALSE,
                      cache = FALSE
                      )
```

@@

```{r}
# Remove unneeded columns and rearrange the remainder
 final_citation_table <- compact_data_with_citation_keys %>% 
     relocate(c('doi', 'year', 'bibtexkey'), .after = title) %>% 
     select(-c(year_aggreg, x0_reviewer, category, 
               number, pages, journal, publisher, 
               volume, language, month, publication_type, 
               modelling_timing, intervention_type, collab_type,
               author, paper_doi, year, 
               doi, bibtexkey
               )
            ) %>% 
     arrange(desc(publication_year))
```

```{r}
# Make a neat table of papers from columns 1(title)-5
final_citation_table %>% 
    select(1:5) %>% 
    kable()

# booktabs = TRUE,
#       longtable = FALSE#,
#       # caption = 'Extracted data per paper: publication_year, author_affiliation_type, country_studied, author_in_country_studied.'
#          ) %>%
#     kable_styling(latex_options = c('striped',
#                                     'scale_down',
#                                     'hold_position',
#                                     'repeat_header'
#                                     )
#                   ) %>%
#     column_spec(column = c(1, 3), width = "5cm") #%>%
    # landscape()
```

<!--  ```{r} -->
<!-- # Make a neat table of papers from columns 1 (title), and 6-10  -->
<!-- final_citation_table %>% -->
<!--   select(c(1, 6:10)) %>% -->
<!--   kable( -->
<!--     booktabs = TRUE, -->
<!--     longtable = FALSE, -->
<!--     caption = "Extracted data per paper: disease, objectives, individual_representation, space_representation, model_structure." -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("striped",  -->
<!--                                   "scale_down",  -->
<!--                                   "hold_position",  -->
<!--                                   "repeat_header" -->
<!--                                   ) -->
<!--                 ) %>% -->
<!--   column_spec(column = c(1), width = "5cm") %>% -->
<!--   landscape() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Make a neat table of papers from columns 1 (title) and 11-15  -->
<!-- final_citation_table %>% -->
<!--   select(1, 11:15) %>% -->
<!--   kable( -->
<!--     longtable = FALSE, -->
<!--     caption = "Extracted data per paper: parametrization, validation, outbreak_type, intervention_modelled, vax_modelled_with_non_vax." -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("striped",  -->
<!--                                   "scale_down",  -->
<!--                                   "hold_position",  -->
<!--                                   "repeat_header" -->
<!--                                   ) -->
<!--                 ) %>% -->
<!--   column_spec(column = c(1, 2, 5), width = "4cm") %>% -->
<!--   landscape() -->
<!-- ``` -->

<!--  ```{r} -->
<!-- # Make a neat table of papers from columns 1 (title) and 16-22 -->
<!-- final_citation_table %>% -->
<!--   select(1, 16:22) %>% -->
<!--   kable( -->
<!--     booktabs = TRUE, -->
<!--     longtable = FALSE, -->
<!--     caption = "Extracted data per paper: is_vax_effective, outcome_measured, sensitivity_analysis, data_used, data_available, simulation_code_available, vax_modelled." -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = c("striped", -->
<!--                                   "scale_down",  -->
<!--                                   "hold_position",  -->
<!--                                   "repeat_header" -->
<!--                                   ) -->
<!--                 ) %>% -->
<!--   column_spec(column = c(1, 3), width = "5cm") %>% -->
<!--   landscape() -->
<!-- ``` -->

>>>>

---
title: "Supplementary material"
output:
  pdf_document:
    fig_crop: no
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      dev = 'png', 
                      out.height = "\\textheight",  
                      out.width = "\\textwidth", 
                      message = FALSE, 
                      warning = FALSE
                      )

options(kableExtra.auto_format = FALSE)
```

@@

```{r}
# Remove unneeded columns and rearrange the remainder
 final_citation_table <- compact_data_with_citation_keys %>% 
     relocate(c('doi', 'year', 'bibtexkey'), .after = title) %>% 
     select(-c(year_aggreg, x0_reviewer, category, 
               number, pages, journal, publisher, 
               volume, language, month, publication_type, 
               modelling_timing, intervention_type, collab_type,
               author, paper_doi, year, 
               doi, bibtexkey
               )
            ) %>% 
     arrange(desc(publication_year)) %>% 
  mutate(num = seq_len(nrow(.))) %>% 
  relocate(num, .before = "title")

# Shorten names

names_dict <- c(year = "publication_year",
                affiliation_type = "author_affiliation_type",
                academic_collab = "purely_academic_collab",
                location = "country_studied",
                interventions = "intervention_modelled"
                )

 final_citation_table <-  final_citation_table %>% 
  rename(names_dict)
```

```{r helper_functions}
#' Function to print the table caption using a template 
#' It extracts the column names and combines them into a comma-separated
#' list and attaches a preceding sentence, which defaults to 
#' ""List of included studies by:""
make_table_caption <- function(df, preceding_sentence = "List of included studies by:"){
  paste(preceding_sentence, paste(names(df)[-c(1)], collapse = ", "))
} 
```
The following table contains information on the data extracted from
each of the included studies.

Technical note: Due to the large number of 
rows, the table could not be printed in one go and was instead printed a few columns 
at a time. In actual fact, it is just a repetition of the title column along with
the presented columns.

```{r cols_1_to_6}
# Make a neat table of papers from columns 1(title)-5
cols_1_to_6 <- final_citation_table %>% 
    select(1:6)

knitr::kable(cols_1_to_6, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_1_to_6)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2), width = "4cm") %>% 
  kableExtra::landscape() 
```

```{r cols_7_to_10}
# Make a neat table of papers from columns 1, 2 (title), and 7-10
cols_7_to_10 <- final_citation_table %>% 
    select(c(1, 2, 7:10))

knitr::kable(cols_7_to_10, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_7_to_10)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

```{r cols_11_to_14}
# Make a neat table of papers from columns 1, 2 (title) and 11-15
cols_11_to_14 <- final_citation_table %>% 
    select(c(1, 2, 11:14))

knitr::kable(cols_11_to_14, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_11_to_14)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

```{r cols_15_to_16}
# Make a neat table of papers from columns 1, 2 (title) and 15-18
cols_15_to_16 <- final_citation_table %>% 
    select(c(1, 2, 15:16))

knitr::kable(cols_15_to_16, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

```{r cols_17_to_18}
# Make a neat table of papers from columns 1, 2 (title) and 19-24
cols_17_to_18 <- final_citation_table %>% 
    select(c(1, 2, 17:18))

knitr::kable(cols_17_to_18, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_1_to_6)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

```{r cols_19_to_20}
# Make a neat table of papers from columns 1, 2 (title) and 19-24
cols_19_to_20 <- final_citation_table %>% 
    select(c(1, 2, 19:20))

knitr::kable(cols_19_to_20, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_1_to_6)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

```{r cols_21_to_22}
# Make a neat table of papers from columns 1, 2 (title) and 19-24
cols_21_to_22 <- final_citation_table %>% 
    select(c(1, 2, 21:22))

knitr::kable(cols_21_to_22, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

```{r cols_23_to_24}
# Make a neat table of papers from columns 1, 2 (title) and 19-24
cols_23_to_24 <- final_citation_table %>% 
    select(c(1, 2, 23:24))

knitr::kable(cols_23_to_24, 
     format = "latex",
     booktabs = TRUE,
     longtable = TRUE
   ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```
